Competing Bandits:\\ The Perils of Exploration under Competition \thanks{This is an extended abstract of \citet{CompetingBandits-merged}, which in turn subsumes conference papers \citet{CompetingBandits-itcs18} and \citet{CompetingBandits-ec19}.}

### 2021-01-16 journal paper/content/sec-intro.tex
small tweaks

\gaedit{While our model allows for the firms to pick from an arbitrary set of algorithms}, we distinguish between three classes of bandit algorithms, based on the prevalent intuition in the area. The distinction concerns the way in which they resolve the fundamental tradeoff between  exploration and \emph{exploitation} (making optimal myopic decisions using the available data). \gaedit{This classification is important for interpreting the equilibrium algorithm choice of the firms as it allows for a ``low" to ``medium" to ``high" technology interpretation. We further use the classification to pick a representative algorithm from each class for our numerical experiments. Going from low to medium to high technology, these three classes are as follows:} \gadelete{Going from more primitive to more sophisticated, these three classes are as follows:}

@@

One model we study is suitable for analysis and another for simulations, but not vice versa. A natural implementation of the \TheoryModel requires running time quadratic in the number of rounds,%
\footnote{\label{fn:Tsquared}\Eg this is because at each round $t$, one needs to recompute, and integrate over, a discrete distribution with $t$ possible values, namely the number of agents that have chosen principal $1$ so far.}
which precludes experiments at a sufficient scale. The \ExptsModel features an intricate feedback loop between algorithms' performance, their reputations and agents' choices, which simplifies the simulations but does not appear analytically tractable.

>>>>

\gaedit{While our model allows for the firms to pick from an arbitrary set of algorithms}, we distinguish between three classes of bandit algorithms, based on the prevalent intuition in the area. The distinction concerns the way in which they resolve the fundamental tradeoff between  exploration and \emph{exploitation} (making optimal myopic decisions using the available data). \gaedit{This classification is important for interpreting the equilibrium algorithm choice of the firms as it allows for a ``low" to ``medium" to ``high" technology interpretation. We further use the classification to pick a representative algorithm from each class for our numerical \gaedit{simulations}. Going from low to medium to high technology, these three classes are as follows:} \gadelete{Going from more primitive to more sophisticated, these three classes are as follows:}

@@

One model we study is suitable for analysis and another for simulations, but not vice versa. A natural implementation of the \TheoryModel requires running time quadratic in the number of rounds,%
\footnote{\label{fn:Tsquared}\Eg this is because at each round $t$, one needs to recompute, and integrate over, a discrete distribution with $t$ possible values, namely the number of agents that have chosen principal $1$ so far.}
which precludes \gaedit{numerical simulations} at a sufficient scale. The \ExptsModel features an intricate feedback loop between algorithms' performance, their reputations and agents' choices, which simplifies the simulations but does not appear analytically tractable.
